\section{Access Control and Security}

\todo{Check that it matches the program/api}
\textbf{Access Matrix for DriveIT System}

\begin{tabular}{|l|*{6}{c|}}\hline
\backslashbox{\miniscule\textbf{Actors}}{\miniscule\textbf{Entities}} & \miniscule\textbf{Car} & \miniscule\textbf{Comment} & \miniscule\textbf{ContactRequest} & \miniscule\textbf{Customer} & \miniscule\textbf{Employee} & \miniscule\textbf{Sale} \\\hline

\miniscule\textbf{Non-registered user} & \miniscule read & \miniscule read && \miniscule create & \miniscule read & \miniscule\\\hline

\miniscule\textbf{Customer} & \miniscule read & \miniscule create & \miniscule create & \miniscule read & \miniscule read & \miniscule read\\
	&& \miniscule read & \miniscule read & \miniscule update &&\\
	&& \miniscule update & \miniscule delete &&& \\
	&& \miniscule delete &&&&\\\hline

\miniscule\textbf{Employee} & \miniscule create & \miniscule read & \miniscule read & \miniscule create & \miniscule read & \miniscule create \\
	& \miniscule read && \miniscule update & \miniscule read && \miniscule read\\
	& \miniscule update && \miniscule delete & \miniscule update && \miniscule update\\
	& \miniscule delete &&&&& \miniscule delete\\\hline

\miniscule\textbf{Administrator} & \miniscule create & \miniscule read & \miniscule read & \miniscule create & \miniscule create & \miniscule create\\
	& \miniscule read & \miniscule delete & \miniscule update & \miniscule read & \miniscule read & \miniscule read\\
	& \miniscule update && \miniscule delete & \miniscule update & \miniscule update & \miniscule update\\
	& \miniscule delete &&& \miniscule delete & \miniscule delete & \miniscule delete\\\hline

\end{tabular}\\\\

Due to the fact that the DriveIT System is available for many users, it is necessary to keep track of which users may have access to specific resources in our system. To keep track of which users got access to which resources, it is necessary to check each user at login, through authentication, to confirm which resources they can access.\\

In our system, a non-registered user (a person accessing the DriveIT homepage without logging in) should be restricted to only be able to search for cars, get a list of employees and create a new user on the homepage.\\

The customer is able to access more on the DriveIT homepage than a non-registered user. The customer is able to access the same information as a non-registered user, but are also able to look through his or her own orders, and also able to create, update or delete his or her own comments on cars.\\

The employee is able to create, update or delete cars, and search for cars. The employee is also able to create a new user (if a person calls the \todo{company using DriveIT?}company using DriveIT for help), get information about a specific user and update a user by request of a customer. The employee is also able to create an order, see the orders of a specific customer, update an order and delete an order. The employee should also be able to get a list of employees, if it is needed in any case.\\

Administrators of the system can do everything the employee can, but also create, update and delete other employees and administrators.

There is a bug in the DriveIT Web Client which means that employees and administrators can login and create comments and contact requests as well. They cannot manage other peoples comments and contact requests though, and also they cannot see own orders and contact requests through the managing menu. Information about employees and administrators cannot be changed through the Web Client, as it was not meant to support this feature.