\subsubsection{UC-5 : Request to get contacted by employee}
\label{request-contact-use-case}
\HRule \\[0.4cm]
% Description
\textbf{Description:} A \texttt{Customer} wants to get contacted by a \texttt{Employee} regarding a specific car. \\
\HRule \\[0.4cm]
% Actors
\textbf{Actors:} \texttt{Employee, Customer}\\
\HRule \\[0.4cm]
% Preconditions
\textbf{Preconditions:} 
\begin{itemize}
    \item The \texttt{Customer} has established connection to the Internet.
    \item The \texttt{Customer} has found a specific car he wants to get contacted regarding and has loaded the detailed view of the car on the \texttt{Web Client}.
    \item The \texttt{Customer} is signed in to the system.
\end{itemize}
\HRule \\[0.4cm]
% Postconditions
\textbf{Postcondition:}
\begin{itemize}
\end{itemize}
    \item The \texttt{Customer} has either been contacted regarding a car or has regret that he wants to get contacted and has deleted the request.
\HRule \\[0.4cm]
% Main success scenarios
\textbf{Main success scenario:}
\begin{enumerate}
    \item The \texttt{Customer} clicks on the `Request to get contacted' button.
    \item The \texttt{Customer} gets notified that he has requested to get contacted regarding the specific car.
    \item If the \texttt{Customer} regrets that he wants to get contacted, he can follow a link on the detailed view for the specific car to see an overview of all his requests and then delete the given request.
    \item Otherwise an \texttt{Employee} will contact the \texttt{Customer} as soon as he sees the request.
\end{enumerate}

\HRule \\[0.4cm]
% Frequency
\textbf{Frequency:}
Daily \\
\HRule \\[0.4cm]

