\subsubsection{UC-2 : Create User Account}
\label{create-account-use-case}
\HRule \\[0.4cm]
% Description
\textbf{Description:} The \texttt{Customer} registers on the \texttt{DriveIT Web Client} \\
\HRule \\[0.4cm]
% Actors
\textbf{Actors:} \texttt{Customer}\\
\HRule \\[0.4cm]
% Preconditions
\textbf{Preconditions:} 
\begin{itemize}
    \item  The \texttt{DriveIT Web Client} is initialised and the device initialising it is connected to the Internet.
    \item  The \texttt{Customer} is on the front page of the \texttt{DriveIT Web Client}.
\end{itemize}
\HRule \\[0.4cm]
% Postconditions
\textbf{Postconditions:}
\begin{itemize}
    \item The \texttt{Customer} has registered an account in the system.
    \item The \texttt{Customer} is able to log in to the system.
\end{itemize}
\HRule \\[0.4cm]
% Main success scenarios
\textbf{Main success scenario:}
\begin{enumerate}
    \item  The \texttt{Customer} wishes to register an account for the \texttt{DriveIT Web Client}.
    \item  The \texttt{Customer} selects 'Register' in the main view of the \texttt{DriveIT Web Client}.
    \item  The \texttt{Customer} fills in his/her e-mail address, first name, last name, phone, and a password. He/she then selects the 'Register' button to save the account.
    \item  If the input is valid, the account is persisted and the \texttt{Customer} is logged in.
\end{enumerate}
\HRule \\[0.4cm]
\textbf{Exception Cases:}
\begin{itemize}
	\item If the phone number is not put in correctly the user will be notified about this.
	\item If the password is not put in correctly the user will be notified about this.
\end{itemize}
\HRule \\[0.4cm]
% Frequency
\textbf{Frequency:}
Hourly \\
\HRule \\[0.4cm]

