\usecase{
    title = {CreateOrder},
    label = uc:createorder,
    description = {The \emph{Employee} creates an order when the \emph{Customer} wants to buy a car.},
%    scope = {},
%    level = {},
    actors = {\emph{Customer}, \emph{Employee}},
%    stakeholders and interests = {},
%    precondition = {},
    preconditions = {
        \item The \emph{Customer} and \emph{Employee} has agreed upon a deal regarding the purchase of a given car.
        \item The \emph{Employee} has the Windows client for the DriveIt system available with Internet connection.
    },
%    postcondition = {},
    postconditions = {
        \item An \texttt{Order} has been successfully created and persisted in the database.
        \item The image belonging to the purchased car is now labelled as \texttt{SOLD}.
    },
    main success scenario = {
        \item The \emph{Employee} opens the `make new order' window.
        \item The \emph{Employee} selects the car that the \emph{Customer} desires to buy and fills in the agreed upon price.
        \item The \emph{Employee} selects the \emph{Customer}\'s profile to get relevant contact information. If the \emph{Customer} has no profile, the \emph{Employee} creates one.
        \item When all the required fields to make a valid \texttt{Order} is filled, the \emph{Employee} clicks the \texttt{CreateOrder} button.
        \item If the car has been sold by another \emph{Employee} in the mean time, the system gives an error message.
    },
%    extensions = {
%        \item 1
%        \item 2
%        \item 3
%    },
%    special requirements = {
%       \item 1
%        \item 2
%       \\
%   },
    frequency of occurrence = Daily,
    %open issues = {},
}