\usecase{
    title = {CreateCar},
    label = uc:createcar,
    description = {The \emph{Employee} Creates a car in the \texttt{DriveIT System} thereby making it available for sale.},
%    scope = {},
%    level = {},
    actors = {Initiated by\emph{Employee}},
%    stakeholders and interests = {},
    preconditions = {
        \item 1 The \emph{Employee} has some information about the new car.
    },
    postconditions = {
        \item 1 The car is in the \texttt{DriveIT System} and is available for sale on the \texttt{DriveIT Webclient}. 
    },
    main success scenario = {
        \item 1 The \emph{Employee} logs into the \texttt{DriveIT System}.
        \item 2 The \emph{Employee} finds the create car view.
        \item 3 The \emph{Employee} Fills data about the car in the view. 
        \item 4 The \emph{Employee} Checks the data and accepts it. The car is now succesfully in the system.
    },
    extensions = {
       \item 1 During item 3 in the main succes scenario, the \emph{Employee} should be able to fill in additional data about the car, by the help of an external system(CarQuery), using the model name.
    },
%    special requirements = {
%	    \item 1
%        \item 2
%		\\
%	},
    frequency of occurrence = Often,
    open issues = {It is unclear if the car should be immediately up for sale or if the \emph{Employee} should be able to choose what "state" the car should be in.}
}
\subsubsection{UC-3 : Create Car}
\label{create_car_use_case}
\HRule \\[0.4cm]
% Description
\textbf{Description:} An \texttt{Employee} uses the \texttt{Windows Client} to create a new car and thereby making it available for sale. \\
\HRule \\[0.4cm]
% Actors
\textbf{Actors:} \texttt{Employee}\\
\HRule \\[0.4cm]
% Preconditions
\textbf{Preconditions:} 
\begin{itemize}
    \item The \texttt{Employee} at least has the manufacturer and model of the car plus at least one picture.
    \item The \texttt{Employee} is signed in to the \texttt{Windos Client} and is connected to the Internet.
\end{itemize}
\HRule \\[0.4cm]
% Postconditions
\textbf{Postcondition:}
\begin{itemize}
    \item The \texttt{Car} is persisted in the database.
    \item The \texttt{Car} is available for sale on the \texttt{Web Client}.
\end{itemize}
\HRule \\[0.4cm]
% Main success scenarios
\textbf{Main success scenario:}
\begin{enumerate}
    \item The \texttt{Employee} signs in to the system.
    \item The \texttt{Employee} chooses the `Car' view and chooses the `Create' button.
    \item The \texttt{Employee} fills out the available data about the car. Given manufactorer and model, the \texttt{Employee} can choose to use the \texttt{Car Query API} to retrieve data about the given car.
    \item The \texttt{Employee} checks that the data is correct and submits the car.
\end{enumerate}
\HRule \\[0.4cm]
% Frequency
\textbf{Frequency:}
A couple of times a week \\
\HRule \\[0.4cm]

