\section{Functional requirements}

\subsection{General Functional Requirements}
\begin{itemize}
	\item The system must be able to support different user roles, more specifically a customer-, employee- and administrator role.
	\item The Windows client must only be accessible to employees and administrators.
    \item It must be possible for customers to browse cars with different filters and criteria.
    \item A customer must be able to create and sign in to a customer account on the web client.
    \item A customer must be able to find contact information for employees without signing in.
    \item A customer must be able to request contact from an employee, if the customer is signed into the system.
    \item A customer must be able to comment on the cars in the system, if signed in.
    \item A customer must be able to edit contact information for his/her account.
    \item An employee must be able create, read, update, and delete all cars in the system.
    \item It must be possible for an employee to create, read and delete several images of a car.
    \item An employee must be able to read, update and delete a list of requests from customers wanting to be contacted regarding a car.
    \item An employee must be able to create a account on behalf of a customer calling the dealership without an existing customer account.
    \item An employee must be able to create, read, update and delete all sales of a car.
    \item A customer must be able to see all cars he has purchased.
    \item An administrator must be able to create, read, update, and delete employees.
    \item It must be possible to browse through the images of a car.
    \item An employee must be able to get more information about a car using the \textit{Car Query API}\footnote{\url{http://www.carqueryapi.com/}}.
    \item A sold car must be visible in the system for another week after it has been sold.
    \item A customer must be able to create, read, and delete all contact requests he/she has made.
    \item Profile pictures of customers and employees should be provided using their \textit{Gravatar}\footnote{\url{https://en.gravatar.com/}} avatar.
\end{itemize}
The group have chosen to design and develop a comment system instead of a rating system for cars.

\subsubsection{Optional Functional Requirements}
The following optional requirements must be fulfilled.
\begin{itemize}
	\item The system must be deployed/hosted on Microsoft Azure.
	\item The system must supports showing several images of a car in an image gallery.
	\item (\textit{Partially}) The system must have a form for a customer to request contact by an employee or let the customer contact the dealership lot by clicking a car.
\end{itemize}

\section{Initial Analysis Objects}
\begin{itemize}
    \item \textbf{Customer:}\\
    A customer is a person interested in buying a car. The customer can only use the web client. A customer object will hold contact information about a given customer e.g. name, email, and phone.
    \item \textbf{Employee:}\\
    An employee is a person working for the used car dealership. The employee uses the Windows client. The employee object will hold information about a given employee e.g. name, email, job title, and phone. Employees can be administrators, meaning that they are able to create, update, and delete employees.
    \item \textbf{Car:}\\
    The car object is a car for sale at the used car dealership. The car object will hold relevant information about itself e.g. manufacturer, model, year, colour, price, etc. The object also has an attribute indicating whether it is sold or not.
    \item \textbf{Sale:}\\
    A sale consists of a car, an employee, and a customer. It uses some different information from each of these objects to make a sale. From the customer's perspective, it is called an order.
    \item \textbf{Comment:}\\
    A comment consists of a customer, a title and a description. A car object can have several comments.
    \item \textbf{Contact Request:}\\
    A contact request will be created when a customer wants to be contacted by an employee regarding a given car. It contains the car in question, the requesting customer and an optional employee when the request is being dealt with.
\end{itemize}
