\section{Sprints}
After each sprint the team sat down for a sprint end meeting. We followed the procedure outlined in the \textit{SCRUM} documentation\footnote{http://en.wikipedia.org/wiki/Scrum_%28software_development%29} on how to carry out the meeting.\\
The main points to consider were \textit{"What Could Be Improved?"}, \textit{"What Went Well?"} and \textit{"Presentation of Work"}.
\subsubsection{Sprint 1: Retrospection}
\label{sec:sprint1}
\small{\textit{Facilitated by Jacob Stenum Czepluch (SCRUM master)}} 

\textbf{What Could Be Improved?}

\begin{itemize}
	\item Mikael would like to be able to see stuff in VS Online. He had no access.
	\item LaTeX is horrible, no one likes using it.
	\item TeX templates are weird and we spent time figuring them out.
	\item Markdown would make (at least Fischer's) life easier. 
	\item LaTeX conventions need to be specified and \textbf{used}. This takes time.
	\item Wind does not want to be the "tex-guy". Everyone needs to LaTeX their own stuff.
\end{itemize}

\textbf{What Went Well?}

\begin{itemize}
	\item Work went well. 
	\item People managed their time well.
	\item The workload will increase when coding starts.
	\item Facebook group worked really well.
	\item Tasks and SCRUM interface online works well.
	\item Graphical online interface gives a nice overview.
	\item Git works, branching is going to be interesting. 
\end{itemize}

\textbf{Presentation of Work}

We have no product owner, so the group therefore pretended to be the group owner while also being the developers of the product. 

All group members have checked the work together, and everything looks the way it should. \\
Minor improvements have either been made or planned and added to the next sprint. 


\subsubsection{Sprint 2: Retrospection}
\label{sec:sprint2}
\small{\textit{Facilitated by Anders Wind Steffensen (SCRUM master)}} 

\textbf{What Could Be Improved?}

\begin{itemize}
	\item Everyone would like a bit more time, but still felt they finished the most important work.
	\item Git branching is okay, some people still don't quite get it, but we have not had any major conflicts.
	\item We forgot the documentation a bit this time, focusing more on code. 
	\item Some group members underestimated the time they thought they would spend to finish a task.
	\item We need to remember to update the SCRUM online tool so that the burndown chart is correct.
	\item Visual Studio can be a bitch. There's too much black magic.
\end{itemize}

\textbf{What Went Well?}

\begin{itemize}
	\item Work went well. We managed to accomplish the major goals (working prototype).
	\item People managed their time well.
	\item Facebook group still works really well.
	\item Git is awesome when it works.
\end{itemize}

\textbf{Presentation of Work}

We have no product owner, so the group therefore pretended to be the group owner while also being the developer of the product.

All group members have checked the work together, and everything looks the way it should.\\
Minor improvements have either been made or planned and added to the next sprint, with mostly the same people assigned.\\
Work people didn't have time to finish have been added to the next sprint.

\subsubsection{Sprint 3: Retrospection}
\label{sec:sprint3}
\small{\textit{Facilitated by Anders Fischer-Nielsen (SCRUM master)}} 

\textbf{What Could Be Improved?}

\begin{itemize}
	\item We need to stay on top of updating the SCRUM tool (VS Online).
	\item We need a better delegation of work. Some group members relaxed a bit. 
	\subitem Better time estimates could fix this.
	\item The placement of big tasks (that affect other parts of the product) should be changed so that these happen at the beginning of the sprint. That should free up other team members so that they are less stressed by the end of a sprint. 
	\item We need to get better at attending the stand up meetings.  
	\item Noone should be working at the SCRUM meetings. \text{NO CODING!}
\end{itemize}

\textbf{What Went Well?}

\begin{itemize}
	\item The group is somewhat following the time frame for the product. We're not \textit{too} far behind so far.
	\item Time estimates are generally okay, everything considered. 
	\item The communication of the group is fine. The Facebook group is working beautifully. 
\end{itemize}

\textbf{Presentation of Work}

We have no product owner, so the group therefore pretended to be the group owner while also being the developer of the product.

Some group members have presented their finished work and eveything that people finished in time looks good.\\
Some tasks were not completed, and did not work, when we tried to show them off. 
Minor improvements have either been planned and added to the next sprint, with mostly the same people assigned.\\
The work group members didn't have time to finish have been added to the next sprint.\\

\subsubsection{Sprint 4: Retrospection}
\label{sec:sprint4}
\small{\textit{Facilitated by Anders Fischer-Nielsen (SCRUM master)}} 

\textbf{What Could Be Improved?}

\begin{itemize}
	\item Assigning tasks completely failed this sprint. Group members worked on whatever they felt was missing.
	\item We need a better delegation of work. Since members had no work assigned, roles were never assigned.
\end{itemize}

\textbf{What Went Well?}

\begin{itemize}
	\item Considering no tasks were delegated all the work was completed without major issues. 
	\item Work was finished in time in a satisfactory manner. Of course there were some things that could have been fixed post-project, but they are outside of the scope. 
\end{itemize}

\textbf{Presentation of Work}

We have no product owner, so the group therefore pretended to be the group owner while also being the developer of the product.

The team went through the finished work together, trying to find any missing requirements. 
No major issues were found. The work was deemed satisfactory (shippable) considering the time frame.
